Response to the defense feedback

### 2021-06-17 Chapter-6/Chapter-6.tex
Updates from Overleaf

Our tool can give a conservative estimation of the
side-channel leakage based on Channel Capacity. The channel capacity
measures the information flow between the source and the
destination. One useful characteristic of channel capacity is not
affected by the input, which is useful because we cannot
assume the input secrets of the software in practice. In Chapter~\ref{chapter5}, we
use the sampling result to approximate the true value of the
channel capacity. We prove the sampling method presented in the chapter can only give the conservative estimation of the amount of the true leakage.

@@

>>>>

\ctool{} can give a conservative estimation of the
side-channel leakage based on Channel Capacity. The channel capacity
measures the information flow between the source and the
destination. One useful characteristic of channel capacity is not
affected by the input, which is useful because we cannot
assume the input secrets of the software in practice. In Chapter~\ref{chapter5}, we
use the sampling result to approximate the true value of the
channel capacity. We prove the sampling method presented in the chapter can only give the conservative estimation of the amount of the true leakage.

@@

\section{Limitations}
The methods in my dissertation cannot find all kinds of side-channel leakages. No
tool can find all forms of leakages. Even for address-based side-channel leakages, \tool{} and \ctool{} cannot find all the leakages due to the code coverage problem. Some verification tools can prove the absence of side-channel leakages for some small code snippets. However, to the best of my knowledge, no tools as yet can prove the absence of side-channel leakages in production software.

The quantification result only applies to specific threat models. For example,
\tool{} quantifies the number of leaked bits during one real execution. So it is
possible that one leakage site leaks little information in one execution but leaks much more information in another execution.

The research in the dissertation can only handle address-based side-channel
attacks. Many side-channel attacks infer secret data based on other side-channel
signals (e.g., timing, EM signals). However, the root cause of many of these attacks is still the same. That is, the program accesses different addresses when it processes different input secrets. Under the circumstance, our methods can still detect these leakage sites.
